\section{Scoring}

The Branch total is the amount of Points minus the amount of Penalties for that Branch. Each Branch is scored separately. The total score for a Match is the sum of these Branch totals. A team’s final score for the day will be the sum of the scores for their best two Matches, ignoring the score for their worst match. 

\subsection{Getting Points}
\begin{itemize}
    \item Container Control: 10 Points for successfully moving one shipping container out of the dock into the correct Branch. 
    \item Container Delivery: 50 Points for delivering a container into its colored zone. The container must be on the ground, not in contact with the robot, and completely within the boundaries of the zone to count as Delivered.
    \item Branch Completion: 20 points when the robot returns to the Dock, Completing the Branch.
    \item Time Bonus: when a Branch is Completed, the team will earn a time bonus equal to 1 point for every 10 seconds left on the clock, rounded down. (i.e., 35 seconds remaining would yield a time bonus of 3 points, while 8 minutes 12 seconds remaining would yield 49 points)
\end{itemize}

\noindent
If a robot is not able to control a shipping container, they may visit a Delivery Zone without the container and return to the Dock, gaining points for Branch Completion. The robot must at least partially enter the Delivery Zone. The team will not gain the Time Bonus or points for Container Delivery.

\subsection{Getting Penalties}
\begin{itemize}
    \item Wall Touch: 1 point will be lost every time the robot touches a wall. This cannot be accrued more than once in a 3-second period, and sustained contact with the wall by a moving robot will accrue another penalty every 3 seconds. A robot that is not moving will only accrue one penalty for the initial wall touch.
    \item Breaking the Field: 10 points will be lost for breaking the field. Anything that required a judge to move things (e.g., walls or obstacles) back into place or use duct tape probably constitutes “breaking the field.” This is up to the judges’ discretion but should be easy to avoid. 
    \item Human Involvement: For a 20 point penalty, the team representative at the field may touch the robot. This could be done to fix a sensor, move a tangled wire, stop it from plowing down a wall, etc. If prolonged touch is necessary to fix something on the bot, only the one penalty will be acquired. The representative may move the robot off the field with judge permission and call team members over to work on it, and when ready may place the bot back on the field in the position it left off. The representative may not touch the shipping container without judge permission. If the robot is holding a shipping container when taken off the field, the judge will place the container on the field in front of the robot, and will not place it back on the robot after it is returned to the field. 

\end{itemize}

\subsection{Restarting}
At any time while working on a Branch, the team representative at the field may announce a Restart, which will move the robot and container back to the Dock and erase all Points and Penalties accrued for that Branch. This will not reset the time, nor will it affect Point Totals of any other Branches. \newline

\noindent
If the shipping container falls out of the field or is otherwise inaccessible by the robot, the team representative may not use a Human Involvement penalty to move it back, but must rather announce a Restart to move the container and robot back to the Dock.
