\section{The Field}

The robot and all shipping containers will start in the Dock. The four shipping containers have designated starting locations within the Dock. The team representative may place the robot anywhere in the Dock as long as it is not in contact with any containers or the walls. Each shipping container will be a unique color, and this color will match the Branch and delivery zone to which it belongs. The driver must transport this colored container to the Delivery Zone at the end of its corresponding Branch. After delivering the container, the robot must return to the Dock for the Branch to be Completed. No autonomous behavior is necessary, though teams may implement autonomous subroutines if they wish. \newline 

\noindent
There are four colored shipping containers and four colored Branches: Red, Blue, Yellow, and Black. These branches can be completed in any order. Each branch will have a unique obstacle or difficulty:  

\begin{itemize}
    \item Red Branch: Tunnel. There are no lights in the tunnel. 
    \item Blue Branch: Slalom. This requires high maneuverability. 
    \item Yellow Branch: Ramp. Even with a shallow slope, this requires high motor power. 
    \item Black Branch: Distance. This branch consists of straightaways that reward robot speed. 
\end{itemize}

ADD PIC \newline

\noindent
All pathways are at least 2 feet wide at all points. All walls (marked in grey) will be 3 inches tall, made of thin wood. Colored areas are the Delivery Zones made of tape. The tunnel has a vertical clearance of 1 foot. The ramp has an angle of 15 degrees and a final height of 8 inches. \newline

\noindent
GET STEPH TO MAKE A PIC WITH DIMENSIONS OF SHIPPING CONTAINER
